Security Metrics for the Android Ecosystem

### 2015-07-23 security_scoring.tex
Reorder abstract to emphasise metrics over particular results

>>>>

\subsection{Utilitarianism}
From a utilitarian standpoint, while small manufacturers like Symphony and Walton do badly on our scores, they do not have as many customers as higher scoring manufacturers.
Hence the total risk to users from the higher scoring popular manufacturers is higher than the risk from the lower scoring unpopular manufacturers.
We could normalise the scores for market penetration and so give a score reflecting the risk posed by that manufacturer's performance, which would tend to decrease the difference between manufacturers in our current scoring.
However we have only considered vulnerabilities affecting all Android devices, not those which are specific to manufacturers and so the aggregation point is all Android, not a specific manufacturer.\todo{Does that even make sense?}
Additionally since our scores are provided so that customers can chose which devices to buy then it is the marginal risk to that individual of that device which is of interest rather than the aggregate risk to all users.
